### 2019-08-01 paper.tex
Full paper on thesis

\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab}

>>>>

\section*{TraMoS V: Updated ephemeris and transit timing variations of the hot Jupiters WASP-18b, WASP-19b and WASP-77Ab\footnote{Copy of paper submitted to A\%A on July 9, 2019.}}
